\papertitle

### 2021-03-04 source_separation/paper/paper.tex
Add to abstract

	\begin{abstract}
		The abstract should be placed at the top left column and should contain about 150-200 words.
	\end{abstract}
	%

>>>>

	\begin{abstract}
		The abstract should be placed at the top left column and should contain about 150-200 words.

		We identify that sound source separation is a pre-processing method that can improve computer-assisted musical orchestration. In this paper, we compare various state-of-the-art models for source separation, including supervised and unsupervised methods, in their effectiveness at improving orchestration. By applying these methods to hand picked target sounds, orchestrating the separated outputs, and comparing them to the orchestration of the same target without separation, we can determine which methods improve orchestration the most. The target sounds we test with are not songs or musical phrases but a collection of atmospheric recordings, sound effects, bells, alarms, and more. These sounds more closely match common targets used in computer-assisted orchestration.  
	\end{abstract}
	%
